Rényi Entropy-Based Heterogeneity Detection in SAR Data

### 2025-03-17 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Update R0-Renyi-entropy-sar.qmd

Following Refs.\ [@Frery2024;@Alpala2024], we also refine the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in \eqref{eq:est_R} using the bootstrap technique to reduce its bias and apply the improved version, denoted as $\widetilde{H}_{\lambda}$:
$$
\widetilde{H}_{\lambda} = 2\widehat{H}_{\lambda}(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{H}_{\lambda}(\bm{Z}^{(b)}),
$$
where $B$ is the number of bootstrap replications, and $\bm{Z}^{(b)}$ is the $b$-th resampled dataset obtained by drawing $n$ observations with replacement from $\bm{Z}$.

>>>>

Following Refs.\ [@Frery2024;@Alpala2024], we refined the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in \eqref{eq:est_R} reducing its bias with bootstrap, obtaining $\widetilde{H}_{\lambda}$:
$$
\widetilde{H}_{\lambda} = 2\widehat{H}_{\lambda}(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{H}_{\lambda}(\bm{Z}^{(b)}),
$$
where $B$ is the number of bootstrap replications, and $\bm{Z}^{(b)}$ is the $b$-th resampled dataset obtained by drawing $n$ observations with replacement from $\bm{Z}$.
